---
title: "Environmental variables clipped by moth collected sites"
output: github_document
---

### Aim
using raster & rgdal package function to clip environmental variables information 

the data we needed:  
1. moth collection sites (GPS)  
2. environmental layers  
    - TCCIP  
    - A GIS-based environmental database of Taiwan and Penghu islands

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(rgdal)
library(rgeos)
library(sp)
library(data.table)

```


```{r moth location}

df_loc = fread('E:/origin_data/species_data/moth/moth_location_information.csv')
df_loc_selec = df_loc[grep('MCE', df_loc$`Site name`)]
coords = df_loc_selec[ , c(10, 9)]

```

## convert csv tp point shpfile layer


```{r csv conver to shp }

loc = SpatialPointsDataFrame(coords = coords, data = df_loc_selec)
crs(loc) = "+proj=longlat +datum=WGS84 +no_defs"

```

## 
```{r}

```

## shp_NG

```{r}

dsn_ng = 'E:/origin_data/environmental layer/A GIS-based environmental database of Taiwan and Penghu islands'
shp_ng = readOGR(dsn = dsn_ng, layer = 'TW_Env_500m_T972_2016_v2')
proj4string(shp_ng) = '+proj=tmerc +lat_0=0 +lon_0=121 +k=0.9999 +x_0=250000 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs'

```

## EarthEnv

```{r}

dsn_Env = 'E:/origin_data/environmental layer/EarthEnv/Habitat heterogeneity'

file_list = grep(list.files(path = dsn_Env), pattern = '.xml', inv = T, value = T)




col_list = c('ENV_Contrast', 'ENV_Correlation', 'ENV_Cv', 'ENV_Dissimilarity','ENV_Entropy', 'ENV_Evenness', 'ENV_Homogeneity', 'ENV_Maximum','ENV_Range', 'ENV_Shannon', 'ENV_Simpson', 'ENV_Std', 'ENV_Uniformity','ENV_Variance')

df_Ear = data.frame(Site_ID = loc$`Site name`)
                     
for (i in c(1:length(file_list))){

layer = raster(paste0(dsn_Env,'/', file_list[i]))

loc_atr_Env = as.data.frame(extract(layer, loc))

colnames(loc_atr_Env) = col_list[i]

df_Ear = cbind(df_Ear, loc_atr_Env)

}

```


## Consensus land cover

```{r}

dsn_land = 'E:/origin_data/environmental layer/EarthEnv/Consensus land cover'

file_list = grep(list.files(path = dsn_land), pattern = '.xml', inv = T, value = T)

col_list = c('ENV_class_1', 'ENV_class_2', 'ENV_class_3', 'ENV_class_4',
             'ENV_class_5', 'ENV_class_6', 'ENV_class_7', 'ENV_class_8', 
             'ENV_class_9', 'ENV_class_10', 'ENV_class_11', 'ENV_class_12'
             )

df_land = data.frame(Site_ID = loc$`Site name`)
                     
for (i in c(1:length(file_list))){

layer = raster(paste0(dsn_land,'/', file_list[i]))

loc_atr_land = as.data.frame(extract(layer, loc, method = 'bilinear'))

colnames(loc_atr_land) = col_list[i]

df_land = cbind(df_land, loc_atr_land)

}


```


## TCCIP

```{r}



```

## over polygon attribute info to point (Environmental variable of NG)

```{r}

df_NG = data.frame(Site_ID = loc$`Site name`)

loc = spTransform(loc, crs(shp_ng))
loc_atr_NG = over(loc, shp_ng[, c(1:100)])

df_NG = cbind(df_NG, loc_atr_NG)

```

## merge df_Ear, df_land and df_NG

```{r}

df_Ear = as.data.frame(df_Ear)
df_land = as.data.frame(df_land)
df_NG = as.data.frame(df_NG)

df_total = merge(df_Ear, df_land, by = 'Site_ID')
df_total = merge(df_total, df_NG, by = 'Site_ID')

write.csv(df_total, 'E:/structure-equation-model-of-moth/result/csv/Env_variables.csv')

```

## moth location clipped Environmental variable of NG

```{r}

over_buffer = function(point, radius, envir){
  buffer = gbuffer(point, witdh = buffer)
  buffer_atr = over(buffer, envir)
  return (buffer_atr)
}

```

